\documentclass{article}
\usepackage[utf8]{inputenc}
%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}

\title{mcellbi-c62 notes}
\author{Myles Fung}
\date{Fall 2022}

\begin{document}

\maketitle

\section{Week 1, 8/22: Course logistics, drugs, poisons, plant medicines, allies, medicine people, shamans. (Poeia 1-27).}

\subsection{subsection title}


\section{Week 2, 8/29: Drugs entering body, basic cell biology, basic neurobiology, nervous system. No poeia.}

\subsection{subsection title}
Fire ecology is riveting.

\begin{itemize}
    \item item 1
    \item item 2
\end{itemize}

\begin{enumerate}
    \item numbered list item
\end{enumerate}



\section{Week 3, 9/6: Solanaceous plant family, alkaloids, hallucinogens, tobacco, nicotine. (Poeia 29-50). }


\section{Week 4, 9/12: Tobacco (concluded), prevalence statistics. Areca/betel nut. 
  Alcohol, fermentation, distillation, toxicities. (Poeia 51-82; 93-97). 
  (HW 2 due in Section). }

\section{Week 5, 9/19: Sedative-hypnotic pharmacology, general anesthetics, inhalants, 
  pharmaceutical sedative-hypnotics. (Poeia 83-92). 
  Absinthe, thujone. (Poeia 99-113). 
  Drug law history, controlled substances (CS), and CS schedules.  }


\section{Week 6, 9/26: Cannabis. (Poeia 177-225). 
  (Debate 1 in Discussion Section). }


\section{Week 7, 10/3: Opium, opioids, and endorphins. (Poeia 117-143). 
  Caffeine, tea, coffee, cacao, chocolate, kola. }


\section{Week 8, 10/10: Midterm Exam One on Tuesday October 11. 
  Coca and cocaine. (HW3 due in Section). }


\section{Week 9, 10/17: Ephedra, khat, amphetamine.  
  Addiction and treatment.  (HW4 due in Section).  }
  
  
\section{Week 10, 10/24: Psychiatric medications, placebo effects and mind-body medicine. 
  (HW5 due in Section). }
  
  
\section{Week 11, 10/31: Mind-body medicine, psychedelics introduction and history, LSD. }
  
  
\section{Week 12, 11/7: Peyote, mescaline, DMT, ayahuasca, magic mushrooms, psilocybin. 
  (Debate 2 in Discussion Section). (Veterans Day Holiday on 11/11) }
 
 
\section{Week 13, 11/14: Synthetic psychedelics, MDMA, clinical research. 
  Psychedelic neuroscience. (HW6 due in Section). }


\section{Week 14, 11/21: Ketamine, nitrous oxide.  (Thanksgiving Holiday) }
  
  
\section{Week 15, 11/28: William James, brain, mind, and reality. 
  Midterm Exam Two on Thursday December 1. 
 }



\end{document}